### 2019-04-03 thesis_proposal_LaTeX/Chapters/5_TheoreticalFramework.tex
2nd draft Done

\subsubsection*{\color{mygray}[Chapter under work]}
% Background and state-of-the-art
% This involves a thorough state-ofthe-art bibliographic review, the building of a formal foundation, the study of related techniques, analysis and awareness of previous works and study of fundamental aspects that can help carry on your research.

@@

\section{Electro-Mechanical Spinning}
Diverse polymer patterning techniques have being develop for the fabrication of nano-fibers, such as arc discharge [22], chemical vapor deposition, laser ablation [23], and vapor growth [21]. Nonetheless, those processes are expensive due to either the low product yield or the expensive equipment required. The electrospinning method can produce fibers with a range of diameters between 10 $n m$ and 10 $\mu m$ [24,25] from a polymer solution under the influence of an electrostatic force. The applied electric field and solution conductivity and viscosity is an important parameter the affects the fiber diameter during the spinning along with other parameters such as jet length, solution viscosity surrounding gas, flow rate and the collector geometry [26-30]. [31-33]

\cite{Nataraj2012}

Two sub-techniques can be derived from electrospinning depending on the distance between the dispensing electrode and the collector. The process in which the electrospun jet can be controlled near the tip is called NFES or near-field electrospinning. \cite{Cisquella-Serra2019} Moreover, if the distance between the collector and the dispensing needle is farther, the configuration is known as FFES or far-field electrospinning. \cite{Nataraj2012}

\section{Carbon nano-wire}
Carbon nano-wires (CMWs) are known as long, thin strings with diameters between 10 and 1 thousand nm; composed mostly by carbon atoms aligned parallel to the long axis of the fiber. \cite{Nataraj2012} Carbon nano-wires are different from carbon nano-tubes, as CMWs are not composed by graphene sheets in cylindrical form. \cite{Nataraj2012}

>>>>

%\subsubsection*{\color{mygray}[Chapter under work]}
% Background and state-of-the-art
% This involves a thorough state-ofthe-art bibliographic review, the building of a formal foundation, the study of related techniques, analysis and awareness of previous works and study of fundamental aspects that can help carry on your research.

@@

\section{Electro-Mechanical Spinning}
Diverse polymer patterning techniques have being develop for the fabrication of nano-fibers, such as arc discharge \cite{Wang2007}, chemical vapor deposition, laser ablation \cite{Ren1998}, and vapor growth \cite{Nadarajah2008}. Nonetheless, those processes are expensive due to either the low product yield or the expensive equipment required. The electrospinning method (invented by Formhals Anton in 1934) can produce fibers with a range of diameters between 10 $n m$ and 10 $\mu m$ \cite{Jayaraman2003,Anton1930} from a polymer solution under the influence of an electrostatic force. The applied electric field and solution conductivity and viscosity is an important parameter the affects the fiber diameter during the spinning along with other parameters such as jet length, solution viscosity surrounding gas, flow rate and the collector geometry \cite{Anton1938,Larrondo1981,Baumgarten1971,Shin2001}.

Even though electrospinning is an old invention \cite{Anton1930}, it is currently a trending topic among researchers \cite{Huang2003,Reneker2008,Schiffman2008}. Some of the reasons electrospinning is to be studied is its potential to fabricate polymer nano-fibers from a variety of polymers. The technique allows the production of thin continuous fibers with ease, with diameters down to 3 $n m$ in some cases, which is something difficult to achieve by other techniques. Furthermore, the basic set-up can be modified with ease to fabricate different fibers with diversified functionalities with different materials. The produced fibers can be aligned or unaligned. Besides, the electrospinning equipment is inexpensive and of small size, compared to the equipment of standard spinning techniques. On the other hand, the understanding of the electrospinning process has improved in the last years \cite{Li2012}. As Reneker and Yarin state: "Electrospinning has rapidly changed fiber making from a capital intensive, large scale process to a low cost, broadly applicable method that manufactures fibers on a laboratory bench, to serve diverse needs ranging from materials science and technology to life sciences and clinical medicine.`` \cite{Reneker2008}

The main components of the electrospinning technique are the fluid control unit (e.g. syringe pump) and a DC power supply. The process also requires a target electrode or combination of electrodes on which the fibers can be collected. Figure \ref{fig:FFES} describes a typical electrospinning set-up. \cite{Li2012}

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/FFES.png}
\decoRule
\caption[Far Field Electrospinning set-up]{Typical far field electrospinning (FFES) set-up \cite{Li2012}.}
\label{fig:FFES}
\end{figure}

Two sub-techniques can be derived from electrospinning depending on the distance between the dispensing electrode and the collector. The process in which the electrospun jet can be controlled near the tip is called NFES or near-field electrospinning. \cite{Cisquella-Serra2019} Moreover, if the distance between the collector and the dispensing needle is farther, the configuration is known as FFES or far-field electrospinning. \cite{Nataraj2012} The difference between NFES and mechano-electrospinning is the presence of a mechanical collector that allows higher pressition when patterning. Figure \ref{fig:NFES} shows a typical near field mechano-electospinning apparatus.

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/NFES.png}
\decoRule
\caption[Near Field Electrospinning set-up]{Typical near field electrospinning (NFES) set-up \cite{Zhu2016}.}
\label{fig:NFES}
\end{figure}

%\section{Pyrolysis}
%

\section{Carbon nano-wire}
Carbon nano-wires (CMWs) are known as long, thin strings with diameters between 10 and 1 thousand $n m$; composed mostly by carbon atoms aligned parallel to the long axis of the fiber. \cite{Nataraj2012} Carbon nano-wires are different from carbon nano-tubes, as CMWs are not composed by graphene sheets in cylindrical form. \cite{Nataraj2012} Carbon nano-wires are typically fabricated by electrospinning and pyrolysis/carbonization as the main processes. During the fabrication process, the polymer molecules are to be crosslinked to prevent melting during the subsequent pyrolysis. The carbonization step removes non-carbonized components in form of condensable and incondensable gases \cite{Basu2018} to then yield carbon structures of about 50\% to 75\% of the mass of the original polymeric structure \cite{Nataraj2012}.
